---
title: "Data Speaks Happiness"
author: "Yu Shen"
date: "2/4/2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
library(gridExtra)
library(RColorBrewer)
library(wordcloud)
```

```{r read data, warning=FALSE, message=FALSE, echo=FALSE}
processed_data <- read_csv("/Users/apple/Documents/GitHub/Spring2019-Proj1-yushen0922/output/processed_moments.csv")
head(processed_data)
names(processed_data)
```

```{r read demo data, warning=FALSE, message=FALSE, echo=FALSE}
demogra_data <- read_csv("/Users/apple/Documents/GitHub/Spring2019-Proj1-yushen0922/data/demographic.csv") ## import demographic data

head(demogra_data)
```

```{r uplodaing data, warning=FALSE, message=FALSE, echo=FALSE}
mydata <- processed_data %>%
  inner_join(demogra_data, by = "wid") %>%
  select(wid, 
         original_hm,
         cleaned_hm,
         gender, 
         marital, 
         parenthood, 
         reflection_period, 
         age, 
         country, 
         ground_truth_category, 
         predicted_category, 
         text) ## merge and select 
head(mydata)
```

```{r cleaning data, warning=FALSE, message=FALSE, echo=FALSE}
#clean data
mydata <- mydata[-c(which(as.numeric(mydata$age)<5),
                    which(as.numeric(mydata$age)>150),## remove 
                    ## some unreasonable age
                 which(is.na(mydata$age)),
                 which(is.na(mydata$marital)),
                 which(is.na(mydata$gender)),
                 which(is.na(mydata$parenthood)),## remove NA
                 which(mydata$age=="prefer not to say"),
                 which(mydata$age=="čá")),]


#changing 60yrs to 60
which(mydata$age=="60yrs")
mydata$age [c(32911,35862,38809)] <- rep("60", 3)
#converting age to numeric
mydata$age <- as.numeric(mydata$age)

```
#Introduction#

**Happiness** is the most debated topic for humankind. with the pressure coming from the study and work. Being happy has become one goal in our daily life. The research for happiness is inevitably an meaningful task for us. 
Happy moment can be different amoong people from different ages, genders, races and relationship status.So, what what make these people happy? Is happiness embodied in physical activity or emotional sentiments? Does youth define happiness from different angles? Do women feel different from men and other genders when it comes to their happy moments? etc.

In this paper, I explored the HappyDB data with more than 100,000 crowd-sourced happy moments. 
```{r}
#basic data statistics and distribution
age_stat <- summary(mydata$age)
## define people with age under 30 is young and above 30 is old
young_num <- length(which(mydata$age <= 30))
old_num <- length(which(mydata$age > 30))
data.frame(young_num,old_num)

male_num <- length(which(mydata$gender=="m"))
female_num <- length(which(mydata$gender=="f"))
male_num/length(mydata$gender)
female_num/length(mydata$gender)


single_num <- length(which(mydata$marital=="single"))
married_num <- length(which(mydata$marital=="married"))
divorced_num <- length(which(mydata$marital=="divorced"))

single_num/length(mydata$marital)
married_num/length(mydata$marital)
divorced_num/length(mydata$marital)
```

The average age is 32 years old with the youngest ones being 17 years old and the oldest being 98 years old. Around 57% are men and 42% are women. Approximately 54% are single, 41% are married,  roughly 4% are divorced and the remaining 1% are either separated or widowed.



##Data Exploration##
In all of the provided data , let's look at how these categories of happiness are distributed:
```{r all categories, warning=FALSE, message=FALSE, echo=FALSE}
category_freq <- count(mydata, predicted_categories=mydata$predicted_category)
category_freq$percent <- round((category_freq$n/sum(category_freq$n))*100, 2)
ggplot(category_freq, aes(predicted_categories, percent)) +
  geom_histogram(stat="identity", color="red", fill="red") +
  labs(x="categories of happiness", y="frequency (%)", title="The Frequency of the 7 Happiness Categories of Happiness") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,10)) +
  geom_text(aes(x=predicted_categories, y=category_freq$percent, label=category_freq$percent,size=1,vjust=-1)) 

```
This sample gives an 7 categories of happiness: 

1. Achievement
2. Affection
3. Bonding
4. Enjoying the Moment
5. Exercise
6. Leisure
7. Nature

From this graph, it looks like people's happiness concentrates significantly around themes of achievement and affection. Enjoying the moment and bonding come 3rd and 4th in rank, respectively. Then, Leisure, nature and exercise come 5th, 6th and 7th in rank. 


```{r total wordcloud, warning=FALSE, message=FALSE, echo=FALSE}
words <-  mydata %>%
  unnest_tokens(word, text)## unnest the text
word_count <- words %>%
  count(word, sort = TRUE)## count the words with rank

##plot a word cloud
set.seed(0)
wordcloud(words = word_count$word, freq = word_count$n, min.freq = 1, max.words=100, random.order=FALSE, rot.per=0.3, colors=brewer.pal(12, "Paired"))

```
These are the most frequently used words to describe lived happy moments. Friend, Time and Family are the top 3 words they use to describe hapiness

Now let's look closer at other information that we have, such as age, gender and relationship status. These variables could tell us different stories about the distribution of these happy moments. Accordingly, I will look further into studying genders, young and old people, marital situations, and parenthood.

##1. Age:##
```{r Age Distribution, warning=FALSE, message=FALSE, echo=FALSE}
ggplot(mydata) +
  geom_bar(aes(x=age, fill=factor(predicted_category))) +
  labs(title="The Distribution of Age", fill="categories of happiness") +
  scale_x_discrete(limits = seq(0,100,5)) +
  scale_y_discrete(limits=seq(0,8000,1000))
```

From this graph, we can tell that the age of the majority of people is between the early 20s and early 40s. We can also see that achievement, affection and bonding are the top 3 categories of happiness.
Then I define the age categories as the following:

1. Younger than 20 years old: early adult
2. 20-40 years old: young adults
3. 41-65 years old: adults
4. Older than 65 years od: seniors

```{r Age Categories, warning=FALSE, message=FALSE, echo=FALSE}
#age categories subsets
early_adult <- mydata [which(mydata$age %in% (17:20)), ] 
young_adult <- mydata [which(mydata$age %in% (20:40)) , ]
adult <- mydata [which(mydata$age %in% (41:65)), ] 
senior <- mydata[which(mydata$age>65),] 
```

```{r happiness categories based on age, warning=FALSE,message=FALSE, echo=FALSE}
#Happiness Categories Given a Population in the Early 20s
freq_early_adult <- count(early_adult, predicted_categories=early_adult$predicted_category)

freq_early_adult$percent <- round((freq_early_adult$n/sum(freq_early_adult$n))*100, 2)

p_early_adult <- ggplot(freq_early_adult, aes(predicted_categories, percent)) +  
  geom_histogram(stat = "identity", fill="blue", color="blue") +  
  labs(x="happiness categories", y="frequency (%)", title="Happy Moments of 17-20 year olds") +  
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +  
  geom_text(aes(x=predicted_categories, y=freq_early_adult$percent, label=freq_early_adult$percent, vjust=-1))

#Happines Categories Given that the Population is a Young Adult (20-40 years old)
freq_young_adult <- count(young_adult, predicted_categories=young_adult$predicted_category)
freq_young_adult$percent <- round((freq_young_adult$n/sum(freq_young_adult$n))*100, 2)

p_young_adult <- ggplot(freq_young_adult, aes(predicted_categories, percent)) +  
  geom_histogram(stat = "identity", fill="pink", color="pink") +  
  labs(x="happiness categories", y="frequency (%)", title="Happy Moments for 20-40 year olds") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +  
  geom_text(aes(x=predicted_categories, y=freq_young_adult$percent, label=freq_young_adult$percent,vjust=-1)) 

#Happines Categories Given that the Population is Adult (41-65 years old)  
freq_adult <- count(adult, predicted_categories=adult$predicted_category)
freq_adult$percent <- round((freq_adult$n/sum(freq_adult$n))*100, 2)

p_adult <- ggplot(freq_adult, aes(predicted_categories, percent)) +  
  geom_histogram(stat = "identity", fill="green", color="green") +  
  labs(x="happiness categories", y="frequency (%)", title="Happy Moments for 41-65 year olds") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +  
  geom_text(aes(x=predicted_categories, y=freq_adult$percent, label=freq_adult$percent, vjust=-1)) 

#Happines Categories Given that the Population is Senior (>65 years old)  
freq_senior <- count(senior, predicted_categories=senior$predicted_category)
freq_senior$percent <- round((freq_senior$n/sum(freq_senior$n))*100, 2)

p_senior <- ggplot(freq_senior, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity", fill="purple", color="purple") +
  labs(x="happiness categories", y="frequency (%)", title="Happy Moments for Seniors (>65)") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) + 
  geom_text(aes(x=predicted_categories, y=freq_senior$percent, label=freq_senior$percent, vjust=-1)) 
```

So let's see how much of importance does each of the happiness categories have in the lives of our aformentioned age groups:
```{r age grid, warning=FALSE, message=FALSE, echo=FALSE}
grid.arrange(p_early_adult,p_young_adult,p_adult,p_senior,ncol=2)

```

Here, we notice a pattern: as people get older, their happiness gets less impacted by accomplishments and short-lived moments (enjoying the moment category). Instead, their happiness gets more influenced by affection moments. Young people seem to find their joy in achievements rather than affection. As for bonding, we see a shift: for instance, for teens and early 20 year olds, bonding represents a significant part of their happiness (14.14%) compared with that for seniors where it represents 8.32%. In fact, such trends sound intuitive: at a certain time and period of life, older people would have become more settled in their lives with their careers and relationships, thus mostly caring for their emotional needs. On the other hand, the young adults are more focused on their academics, career and living conditions. The following graphs show the difference and similarity of the most frequent words used by adults between 20 and 40 years and seniors.

```{r adult achievement bag of words, warning=FALSE, message=FALSE, echo=FALSE}
#achievement for adults
achievement_data_adult <- young_adult[which(young_adult$predicted_category=="achievement"),]
words_achievement_adult <-  achievement_data_adult %>%
  unnest_tokens(word, text)
word_count_achievement_adult <- words_achievement_adult %>%
  count(word, sort = TRUE)

p1 <- ggplot(head(word_count_achievement_adult,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity", col="black", fill="light blue") +
  labs(x="Words", y="Counts", title="Adults 20-40") +
  coord_flip() 
```

```{r senior achievement bag of words, warning=FALSE, message=FALSE, echo=FALSE}
#achievement for seniors
achievement_data_senior <- senior[which(senior$predicted_category=="achievement"),]
words_achievement_senior <-  achievement_data_senior %>%
  unnest_tokens(word, text)

word_count_achievement_senior <- words_achievement_senior %>%
  count(word, sort = TRUE)
p2 <- ggplot(head(word_count_achievement_senior,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity", col="black", fill="light green") +
  labs(x="Words", y="Counts", title="Seniors")+
  coord_flip() 

grid.arrange(p1,p2, nrow=1,ncol=2)
```

We can see that the happiness stemming from accomplishment for adults between 20 and 40 years old is related to job, money and promotion. Seniors have almost the similar but also different frequent words; evidently the concerns of the two age groups is different given they're at different life stages. Senior care more about life quility such as cars and jobs is not as so important for them as young people
Next Step is analyze genders and see if one has a different say from the other as regards moments of happiness.

##2. Gender:##
In this regard, I will study the two prominent genders in the data: female and male (I will use women and men as labels)
```{r women, warning=FALSE, message=FALSE, echo=FALSE}
#what categories are most women happy with
women_data <- mydata[mydata$gender=="f",]
freq_women <- count(women_data,predicted_category = women_data$predicted_category)
freq_women$percent <- round((freq_women$n / sum(freq_women$n))*100,2)## freq and percent

p_women <- ggplot(freq_women, aes(predicted_category, percent)) +
  geom_histogram(stat = "identity", fill="purple", color="purple") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_category, y=freq_women$percent, label=freq_women$percent, vjust=-1)) +
  labs(x="Happiness Categories", y="Frequency (%)", title = "Distribution of Happy Moments of Women")
```

```{r men, warning=FALSE, message=FALSE, echo=FALSE}
men_data <- mydata[mydata$gender=="m",]
freq_men <- count(men_data,predicted_category = men_data$predicted_category)
freq_men$percent <- round((freq_men$n / sum(freq_men$n))*100,2)

p_men <- ggplot(freq_men, aes(predicted_category, percent)) +
  geom_histogram(stat = "identity", fill="orange", color="orange") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_category, y=freq_men$percent, label=freq_men$percent, pos=2, vjust=-1)) +
  labs(x="Happiness Categories", y="Frequency (%)", title = "Distribution of Happy Moments of Men")
```

```{r gender grid, warning=FALSE, message=FALSE, echo=FALSE}
grid.arrange(p_women,p_men,nrow=1,ncol=2)
```

Interestingly, moments of affection seem to significantly highlight women's happiness (40.91%) more than moments of achievement do. Men's happiness seems to concentrate around achievement (36.68%), then affection (29%) then enjoying the moment and bonding (11.66% and 11.21% respectively). So what words did they frequently use to describe this?

```{r womencloud, warning=FALSE, message=FALSE, echo=FALSE}
#women
words_women <-  women_data %>%
  unnest_tokens(word, text)
word_count_women <- words_women %>%
  count(word, sort = TRUE)
plot_women_words <- ggplot(head(word_count_women,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Most Frequent Terms for Women")+
  coord_flip() 
```

```{r mencloud, warning=FALSE, message=FALSE, echo=FALSE}
#men
words_men <-  men_data %>%
  unnest_tokens(word, text)
word_count_men <- words_men %>%
  count(word, sort = TRUE)
plot_men_words <- ggplot(head(word_count_men,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Most Frequent Terms for Men")+
  coord_flip() 

```

```{r gender frequent terms grid, warning=FALSE, message=FALSE, echo=FALSE}
grid.arrange(plot_women_words,plot_men_words, nrow=1,ncol=2)
```

The previously demonstrated disparities suggest that men and women have their own relative perspective of happiness. Men are driven by accomplishments more than affection, as opposed to women. 
Next,let's explore the marital status of the individuals in our data.

##3. Marital Status:##
```{r marital data, warning=FALSE, message=FALSE, echo=FALSE}
#how many marital status
marital_status <- unique(mydata$marital)

#is there a better way to aggregate than just doing this 
single <- mydata[mydata$marital=="single",] 
df_single <- count(single, predicted_categories=single$predicted_category)
df_single$percent <- round((df_single$n/sum(df_single$n))*100,2)

p_single <- ggplot(df_single, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity") +
  labs(x="happiness categories", y="frequency (%)", title="Single People") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_categories, y=df_single$percent, label=df_single$percent, pos=2, vjust=-1))


########
married <- mydata[mydata$marital=="married",]
df_married <- count(married, predicted_categories=married$predicted_category)
df_married$percent <- round((df_married$n/sum(df_married$n))*100,2)

p_married <- ggplot(df_married, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity") +
  labs(x="happiness categories", y="frequency (%)", title="Married People") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_categories, y=df_married$percent, label=df_married$percent, pos=2, vjust=-1)) 

########  
divorced <- mydata[mydata$marital=="divorced",] 
df_divorc <- count(divorced, predicted_categories=divorced$predicted_category)
df_divorc$percent <- round((df_divorc$n/sum(df_divorc$n))*100,2)

p_divorced <- ggplot(df_divorc, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity") +
  labs(x="happiness categories", y="frequency (%)", title="Divorced People") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_categories, y=df_divorc$percent, label=df_divorc$percent, pos=2, vjust=-1))

########
separated <- mydata[mydata$marital=="separated",] 
df_sep <- count(separated, predicted_categories=separated$predicted_category)
df_sep$percent <- round((df_sep$n/sum(df_sep$n))*100,2)

p_sep <- ggplot(df_sep, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity") +
  labs(x="happines categories", y="frequency(%)", title="Separated People") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_categories, y=df_sep$percent, label=df_sep$percent, pos=2, vjust=-1)) 

######
widowed <- mydata[mydata$marital=="widowed",] 
df_widow <- count(widowed, predicted_categories=widowed$predicted_category)
df_widow$percent <- round((df_widow$n/sum(df_widow$n))*100,2)

p_widow <- ggplot(df_widow, aes(predicted_categories, percent)) +
  geom_histogram(stat = "identity") +
  labs(x="happiness categories", y="frequency", title="Widowed People") +
  scale_y_continuous(limits=c(0,100), breaks = seq(0,100,5)) +
  geom_text(aes(x=predicted_categories, y=df_widow$percent, label=df_widow$percent, pos=2, vjust=-1)) +
  theme(text=element_text(size=9), axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r marital grid, warning=FALSE, message=FALSE, echo=FALSE}
grid.arrange(p_single,p_married,ncol=2)
grid.arrange(p_divorced,p_sep,ncol=2)
```
Achievement is more important for single people than for married people. Overall, affection and achievement followed by bonding and living the moment seem to define people's happiness. 
Now, I will consider a combination of factors: age, gender, marital status, and parenthood.

##4. Personas:##
Let's consider two different profiles for both women and men: the profiles are of same age but one is single with no children and the other is married. I would like to see if marital status and having children has any impact in altering one's perspective of happiness.

```{r parenthood data, warninΩg=FALSE, message=FALSE,echo=FALSE, echo=FALSE}

#Single Adult Women 
single_young_adult_women <- 
  filter(young_adult,gender=="f" & marital=="single" & parenthood=="n")

#Married Adult Mom

married_young_adult_mom <-
  filter(young_adult,gender=="f" & marital=="married" & parenthood=="y")

#Single Adult Men
single_young_adult_men <- 
  filter(young_adult, gender=="m" & marital=="single" & parenthood=="n")

#Married Adult Father

married_young_adult_father <- 
  filter(young_adult, gender=="m" & marital=="married" & parenthood=="y")
```

```{r parenthood first plot,  warning=FALSE, message=FALSE, echo=FALSE}
#plots
affection_data_single_women <- single_young_adult_women[which(single_young_adult_women$predicted_category=="affection"),]
bag_of_words_affection_single_women <-  affection_data_single_women %>%
  unnest_tokens(word, text)
word_count_affection_single_women <- bag_of_words_affection_single_women %>%
  count(word, sort = TRUE)
single_women <- ggplot(head(word_count_affection_single_women,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Single Adult Women (25-40)") +
  coord_flip()
##
affection_data_married_mom <- married_young_adult_mom[which(married_young_adult_mom$predicted_category=="affection"),]
bag_of_words_affection_married_mom <-  affection_data_married_mom %>%
  unnest_tokens(word, text)

word_count_affection_married_mom <- bag_of_words_affection_married_mom %>%
  count(word, sort = TRUE)
married_mom <- ggplot(head(word_count_affection_married_mom,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Married Adult Moms (25-40)") +
  coord_flip()

##
affection_data_single_men <- single_young_adult_men[which(single_young_adult_men$predicted_category=="affection"),]
bag_of_words_affection_single_men <-  affection_data_single_men %>%
  unnest_tokens(word, text)

word_count_affection_single_men <- bag_of_words_affection_single_men %>%
  count(word, sort = TRUE)
single_men <- ggplot(head(word_count_affection_single_men,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Single Adult Men (25-40)") +
  coord_flip()

##
affection_data_married_father <- married_young_adult_father[which(married_young_adult_father$predicted_category=="affection"),]
bag_of_words_affection_married_father <-  affection_data_married_father %>%
  unnest_tokens(word, text)

word_count_affection_married_father <- bag_of_words_affection_married_father %>%
  count(word, sort = TRUE)
married_father <- ggplot(head(word_count_affection_married_father,20), aes(x=reorder(word,n), y=n)) +
  geom_bar(stat="identity") +
  labs(x="Words", y="Counts", title="Married Adult Father (25-40)") +
  coord_flip()

grid.arrange(single_women,married_mom, ncol=2) 

grid.arrange(single_men,married_father, ncol=2) 
```

It is interesting to see how children and the husband represent a big part of a married mother's happy affection moments. On the other hand, single adult women's happiness are dominantly defined by their boyfriend, family and pets. The same applies for the comparison between single adult men and married adult fathers, i.e gender does not make much difference in this situation.

**Summary**
As you grow in age, your definition of happiness change.
Children are a source of joy to mothers same as fathers. Affection is the highlight of married adult individuals. And if you are a single adult woman or man, you're most likely going to find your happiness in your achievement, but you will also find it in affection and essentially with a significant other or family. Ultimately, gender does not alter the perception of happiness necessarily, as we've seen both men and women  define their happiness almost similarly under similar life situations.


**References**
1. https://github.com/rit-public/HappyDB